Biologically-Constrained Region Merging for Connectome Reconstruction

### 2018-03-14 papers/eccv2018/0_introduction.tex
fix typos
added HP comments

% \begin{figure}[t!]
% 	\centering
% 	\includegraphics[width=\linewidth]{./figures/teaser_v2.png}
% 	\caption{Our proposed framework uses both local and global biological constraints to improve an input segmentation.}
% 	\label{fig:teaser}
% \end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=\linewidth]{./figures/bc/teaser_bc_v2.pdf}
	\caption{Biological constraints for 3D segments in Connectomics.}
	\label{fig:biological_constraints}
\end{figure}

The field of connectomics considers the problem of reconstructing the wiring diagram of the brain at nanometer resolutions to enable new insights into the workings of the brain~\cite{haehn2017scalable,kasthuri2015saturated}. 
%Recent advancements in image acquisition using multi-beam serial-section electron microscopy (sSEM) allow researchers to produce terabytes of image data per hour~\cite{hildebrand2017whole}. 
%It is infeasible for domain experts to manually reconstruct this vast amount of image data~\cite{haehn2014design}. 
State-of-the-art automatic 3D reconstruction approaches use pixel-based convolutional neural networks (CNNs) and watershed transforms to generate initial over-segmentation, followed by region merging steps~\cite{seymour2016rhoananet,lee2015recursive,nunez2014graph,parag2017anisotropic,ronneberger2015u,zlateski2015image}.
For the region merging, most methods do not use prior biological knowledge of the 3D shape of neural structures.
Reported on small-sized volumes, a simple threshold-based mean agglomeration method can achieve superhuman result~\cite{lee2017superhuman}.
However, it is unclear if that is the case for larger volumes.
\TODO{sth. about figure 1.}

%\TODO{the selling point is to add biological constraint}
%We present a \textit{top-down graph-based} method that builds on the outputs of bottom-up pixel-based segmentation approaches. 
We present a new region merging framework that imposes both local and global biological constraints onto the output segmentation to match the underlying structure of neuronal processes.
We first extract skeletons from labels in the input segmentation and generate a simplified graph (Fig.~\ref{fig:teaser_pipeline}a). 
Next, we train a CNN classifier to learn biological constraints on the local structural shape of a neuron (Fig.~\ref{fig:teaser_pipeline}b).
This classifier produces probabilities that two segments belong to the same neuron based on the input shapes of the segments.
These probabilities correspond to edge weights in our graph extracted from the input segmentation.
We then use a graph optimization algorithm to partition the graph into a final improved reconstruction by enforcing domain-specific topological constraints from biology (Fig.~\ref{fig:teaser_pipeline}c).

@@

This work makes three contributions:
first, a novel top-down framework that extracts graphs from skeletonized 3D segmentations for improved neural reconstruction of connectomics data; 
next, a region-based CNN classifier to detect errors; 
%(3) an empirical evaluation of our method on several connectomics datasets;  % this is not contribution
last, improved performance over a state-of-the-art pixel-based reconstruction approach on average by \TODO{XX}\% with suitable running times.

>>>>

% \begin{figure}[t!]
% 	\centering
% 	\includegraphics[width=\linewidth]{./figures/teaser_v2.png}
% 	\caption{Our proposed framework uses both local and global biological constraints to improve an input segmentation.}
% 	\label{fig:teaser}
% \end{figure}
\begin{figure}[t!]
	\centering
	\includegraphics[width=\linewidth]{./figures/teaser_v4.png}
	\caption{Our framework uses both geometric and topological biological constraints for region merging. We (a) generate a simplified graph from the skeleton representation of the input segmentation, (b) train a classifier to learn the edge weight based on the shape of the segment connection, and (c) perform graph partitioning with acyclic constraints.}
	\label{fig:teaser_pipeline}
\end{figure}

The field of connectomics considers the problem of reconstructing the wiring diagram of the brain at nanometer resolutions to enable new insights into the workings of the brain~\cite{haehn2017scalable,kasthuri2015saturated}. 
%Recent advancements in image acquisition using multi-beam serial-section electron microscopy (sSEM) allow researchers to produce terabytes of image data per hour~\cite{hildebrand2017whole}. 
%It is infeasible for domain experts to manually reconstruct this vast amount of image data~\cite{haehn2014design}. 
State-of-the-art automatic 3D reconstruction approaches use pixel-based convolutional neural networks (CNNs) and watershed transforms to generate initial over-segmentation, followed by region merging steps~\cite{seymour2016rhoananet,lee2015recursive,nunez2014graph,parag2017anisotropic,ronneberger2015u,zlateski2015image}.
For region merging, most methods do not use prior biological knowledge of the 3D shape of neural structures.
Simple threshold-based mean agglomeration methods can achieve superhuman resolution  small-sized volumes~\cite{lee2017superhuman}.

%\TODO{the selling point is to add biological constraint}
%We present a \textit{top-down graph-based} method that builds on the outputs of bottom-up pixel-based segmentation approaches. 
There are two types of errors in connectomics segmentations.
In a \textit{split error}, multiple segments compose a single neuronal process. 
In a \textit{merge error}, two neurons incorrectly merge to form a single segment. 
Generally, it is much more difficult to correct merge errors than to correct split errors, as the space of possible split proposals grows quickly~\cite{parag2015properties}.
Thus, most reconstruction approaches are tuned towards over-segmentation with many more split than merge errors.
We focus on correcting these split errors in the input segmentation.

We present a new region merging framework that imposes both local and global biological constraints onto the output segmentation to match the underlying structure of neuronal processes.
We first extract skeletons from labels in the input segmentation and generate a simplified graph (Fig.~\ref{fig:teaser_pipeline}a). 
Next, we train a CNN classifier to learn biological constraints on the local structural shape of a neuron (Fig.~\ref{fig:teaser_pipeline}b).
This classifier produces probabilities that two segments belong to the same neuron based on the input shapes of the segments.
These probabilities correspond to edge weights in our graph extracted from the input segmentation.
We then use a graph optimization algorithm to partition the graph into a final improved reconstruction by enforcing domain-specific topological constraints from biology (Fig.~\ref{fig:teaser_pipeline}c).

@@

This work makes three contributions:
first, a novel top-down framework that extracts graphs from skeletonized 3D segmentations for improved region merging for neural reconstruction of connectomics data; 
next, a region-based CNN classifier to detect split errors; 
%(3) an empirical evaluation of our method on several connectomics datasets;  % this is not contribution
last, improved performance over a state-of-the-art pixel-based reconstruction approach on average by \TODO{XX}\% while maintaining scalable runtimes for large volumes.

### 2018-03-14 papers/eccv2018/2_method.tex
added HP comments

% !TEX root =  paper.tex
\begin{figure}[t!]
	\centering
	\includegraphics[width=\linewidth]{./figures/teaser_v4.png}
	\caption{Our proposed framework uses both local and global biological constraints to improve an input segmentation. We generate a simplified graph from an input segmentation (a), train a classifier to learn neuron shape constraints locally (b), and perform graph partitioning to enforce domain-specific properties globally.}
	\label{fig:teaser_pipeline}
\end{figure}
\section{Method}
%\begin{figure*}[t!]
%	\begin{center}
%		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/multicut_input.png}}
%		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/pre-multicut.png}}
% 		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/multicut-graph.png}}
% 		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/post-multicut.png}}
% 	\end{center}
% 	\caption{Outline of our approach, from left to right: result of the pixel-based segmentation and agglomeration algorithm; segments of several neurons from the initial segmentation; extracted skeletonized network of those segments; improved 3D reconstruction of the selected segments after graph construction and partitioning with constraints.}
% 	\label{fig:overview}
% \end{figure*}

@@

Our pipeline is illustrated in Fig.~\ref{fig:teaser_pipeline}.
From the input segmentation we generate a graph $G$ with nodes $N$ and edges $E$ with weights $w_e$. 
The nodes correspond to labeled segments from the input data with edges between merge candidates.
We propose the following three steps to formulate and then partition the graph while obeying constraints from the underlying biology.
First, we only consider merging segments based on a skeletonized representation of the input segmentation (Fig.~\ref{fig:teaser_pipeline}a).
This is enables us to reduce the number of nodes in the graph based on prior knowledge of the shape of neuronal processes.
Second, we train a convolutional neural network that learns biological constraints based on the shapes of the input segmentation (Fig.~\ref{fig:teaser_pipeline}b).
This network generates probabilities that segments belong to the same neuron based only on the segmentations. 
An example of one such learned constraint is that neurons have small turning radii (Fig.~\ref{fig:turn-radii}).
Third, we partition the graph using a lifted multicut formulation with additional acyclic constraints to enforce global biological constraints (Fig.~\ref{fig:teaser_pipeline}c).
The lifted multicut solution is globally consistent which we then augment to produce a tree-structured graph (i.e., one with no cycles).

@@

\begin{figure}[t]
	\centering
	\begin{minipage}{0.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/skeleton1.png}		
	\end{minipage}
	\hfill
	\begin{minipage}{0.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/skeleton2.png}		
	\end{minipage}
	\begin{minipage}{0.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/skeleton3.png}		
	\end{minipage}
	\hfill
	\begin{minipage}{0.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/skeleton4.png}		
	\end{minipage}
	\caption{Example skeletons (in black) extracted from segments using a variant of the TEASER algorithm.}
	\label{fig:skeletonization}
\end{figure}

%A typical approach for generating edges produces one between all adjacent segments. 
%Two segments $l_1$ and $l_2$ are considered adjacent if there is a pair of adjacent voxels with one labeled $l_1$ and the other labeled $l_2$.
%For example, pixel-based agglomeration methods such as mean agglomeration~\cite{lee2017superhuman} or waterz~\cite{funke2017deep} consider all pairs of adjacent segments for merging.
%However, this method produces too many edges in the graph for graph-based optimization approaches. 
Our key observation is that if two segments belong to the same neuronal process, their skeleton end points should satisfy certain geometric constraints.
To extract the skeleton from each segment, we use a variant~\cite{zhao2014automatic} of the TEASER algorithm~\cite{sato2000teasar}. 
This skeletonization algorithm repeatedly uses Dijkstra's algorithm to find the farthest voxel from a seed location. 
Since this algorithm is non-linear in the number of voxels, we downsample the datasets so that there are voxel samples every $\SI{30}{\nano\meter}$ in each dimension.
Empirically, this reduced the running time for skeletonization by $30\times$, with minimal reduction in skeleton accuracy (${\sim}5\%$ fewer branches). 
Fig.~\ref{fig:skeletonization} shows four examples of extracted skeletons (in black). 
These skeletons consist of a sequence of \textit{joints}, locations that are locally a maximum distance from the segment boundary, with line segments connecting successive joints. 
We refer to joints that have only one connected neighbor as \textit{endpoints}. 
We find that approximately 70\% of the segments that are erroneously split have nearby endpoints (Fig.~\ref{fig:merge_candidates}).

Two segments, $s_1$ and $s_2$, receive a corresponding edge if the two following conditions hold.
First, a endpoint in either $s_1$ or $s_2$ is with $t_{low}$ nm of any voxel in the other segment.
Second, there is an endpoint in $s_1$ and an endpoint in $s_2$ that are within $t_{high}$ nm of each other.
We store the midpoints between the two endpoints as the center of the potential merge in the set $\mathbb{S}_c$. 
This algorithm produces a set of segments to consider for merging. 
Only these pairs have a corresponding edge in the constructed graph.
These parameters follow empirically from noise in the skeleton generation process. 
There are occasionally spurious branches and other artifacts and these thresholds mitigate the influence of these degenerate locations.
We provide a fuller analysis in the supplemental materials.

\begin{figure}[t]
	\begin{minipage}{0.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/constraint_error.png}
	\end{minipage}
	\hfill
	\begin{minipage}{0.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/constraint_success.png}
	\end{minipage}
	\caption{Two example candidates for merging. The two segments in the left example do not belong to the same neuron as evidenced by the sharp turning radius.}
	\label{fig:turn-radii}
\end{figure}
\subsection{Learning-based Edge Weight}
\label{sec:edge-weights}
We assign an edge weight $w_e$ to each edge corresponding to the probability that two nodes belong to the same neuronal process.
We train a 3D CNN model to learn these geometric constraints for valid connection between two segments from labeled volume.
\\~\\
\noindent\textbf{Edge Probability}
To predict the probabilities that two segments belong to the same neuron, we train a feed-forward convolutional network with three \textit{VGG-style} convolution blocks~\cite{chatfield2014return} and two fully connected layers before the final sigmoid activation.

For the input of the network, we extract a cubic region of interest (ROI) around each endpoint $e$ in $\mathbb{S}_c$ as input to the CNN. 
The CNN receives three input channels for every voxel in the ROI around segments $l_1$ and $l_2$. 
The input in all of the channels is in the range $\{-0.5, 0.5\}$. 
The first channel is $0.5$ only if the corresponding voxel has label $l_1$. 
The second channel is $0.5$ only if the corresponding voxel has label $l_2$. 
The third channel is $0.5$ if the corresponding voxel is either $l_1$ or $l_2$.
We do not use the raw EM image information to avoid the need to retrain the network on datasets that have been stained differently or imaged at different resolution. 
This reduces the need for generating costly manually-labeled ground truth. 
\\~\\
\noindent\textbf{Edge Weight} Given the probability that the nodes belong to the same neuron is $p_e$, the edge weight $w_e$ is defined as
%p_e &=\mbox{CNN}(x_1, x_2) \\
\begin{align}
w_e = \log{\frac{p_e}{1 - p_e}} + \log{\frac{1 - \beta}{\beta}},
\end{align}
where $\beta$ is a tunable parameter that encourages over- or under-segmentation. 
This particular weighting scheme allows us to optimize for a Bayesian network defined on the graph~\cite{keuper2015efficient,andres2011probabilistic}.

@@

After graph construction, we segment the graph into a globally consistent manner while enforcing topological constraints on the output.
\\~\\
%\subsubsection{Lifted Multicut}
\noindent\textbf{Lifted Multicut}
After constructing the graph we seek to partition it into labels where every label corresponds to a neuronal process. 
We formulate this graph partitioning problem as a multicut problem.
There are two primary benefits to using a multicut formulation. 
First, the number of segments in the final graph is not predetermined but depends on the input. 
Second, this minimization produces globally consistent solutions (i.e. a boundary remains only if the two corresponding nodes belong to unique segments)~\cite{keuper2015efficient}.

We apply the algorithms of Keuper et al.~\cite{keuper2015efficient} to produce a feasible solution to the multicut problem using greedy additive edge contraction.
Following their example, we employ the generalized ``lifted'' multicut formulation.
Traditional multicut solutions only consider the probabilities that two adjacent nodes belong to the same segment. 
In the ``lifted'' extension to the problem, we can penalize non-adjacent nodes that belong to different segments. 
These penalties between non-adjacent nodes are called ``lifted'' edges. 
Ideally these ``lifted'' weights represent the probability that two nodes belong to the same neuron.
However, determining such probabilities is computationally expensive.
We approximate these probabilities by finding the maximal probable path between any two nodes using Dijkstra's algorithm~\cite{keuper2015efficient}.
This is an underestimate of the probability that two nodes belong to the same neuron since it does not consider all possible paths.
Since our graphs are sufficiently small, we can generate ``lifted'' edges between all pairs of nodes. 
\\~\\
%\subsubsection{Topological Constraints}
\noindent\textbf{Topological Constraints}
By reformulating the segmentation problem as a graph partitioning one, we can enforce some global constraints on our result based on the underlying biology.
Traditional hierarchical clustering algorithms do not rely on such constraints but consider local decisions independently.
We enforce a global constraint that neurons are tree-structured and should not contain cycles. 
The multicut problems returns a series of ``collapsed'' edges between nodes that belong to the same neuron.
We iterate over these edges in order of the probability of merge generated by our CNN. 
We ``collapse'' an edge only if it does not create a cycle in the graph.

>>>>

% !TEX root =  paper.tex

\section{Method}
%\begin{figure*}[t!]
%	\begin{center}
%		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/multicut_input.png}}
%		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/pre-multicut.png}}
% 		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/multicut-graph.png}}
% 		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/post-multicut.png}}
% 	\end{center}
% 	\caption{Outline of our approach, from left to right: result of the pixel-based segmentation and agglomeration algorithm; segments of several neurons from the initial segmentation; extracted skeletonized network of those segments; improved 3D reconstruction of the selected segments after graph construction and partitioning with constraints.}
% 	\label{fig:overview}
% \end{figure*}

@@

Our method is illustrated in Fig.~\ref{fig:teaser_pipeline}.
From the input segmentation we generate a graph $G$ with nodes $N$ and edges $E$ with weights $w_e$. 
The nodes correspond to labeled segments from the input data with edges between merge candidates.
We propose the following three steps to formulate and then partition the graph while obeying constraints from the underlying biology.
First, we only consider merging segments based on a skeletonized representation of the input segmentation (Fig.~\ref{fig:teaser_pipeline}a).
This is enables us to reduce the number of nodes in the graph based on prior knowledge of the shape of neuronal processes.
Second, we train a convolutional neural network that learns biological constraints based on the shapes of the input segmentation (Fig.~\ref{fig:teaser_pipeline}b).
This network generates probabilities that segments belong to the same neuron based only on the segmentations. 
An example of one such learned constraint is that neurons have small turning radii (Fig.~\ref{fig:turn-radii}).
Third, we partition the graph using a lifted multicut formulation with additional acyclic constraints to enforce global biological constraints (Fig.~\ref{fig:teaser_pipeline}c).
The lifted multicut solution is globally consistent which we then augment to produce a tree-structured graph (i.e., one with no cycles).

@@

\begin{figure}[t]
	\centering
	\begin{minipage}{0.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/skeleton1.png}		
	\end{minipage}
	\hfill
	\begin{minipage}{0.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/skeleton2.png}		
	\end{minipage}
	\begin{minipage}{0.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/skeleton3.png}		
	\end{minipage}
	\hfill
	\begin{minipage}{0.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/skeleton4.png}		
	\end{minipage}
	\caption{Example skeletons (in black) extracted from segments using a variant of the TEASER algorithm~\cite{sato2000teasar}.}
	\label{fig:skeletonization}
\end{figure}

%A typical approach for generating edges produces one between all adjacent segments. 
%Two segments $l_1$ and $l_2$ are considered adjacent if there is a pair of adjacent voxels with one labeled $l_1$ and the other labeled $l_2$.
%For example, pixel-based agglomeration methods such as mean agglomeration~\cite{lee2017superhuman} or waterz~\cite{funke2017deep} consider all pairs of adjacent segments for merging.
%However, this method produces too many edges in the graph for graph-based optimization approaches. 
Our key observation is that if two segments belong to the same neuronal process, their skeleton end points should satisfy certain geometric constraints.
To extract the skeleton from each segment, we use a variant~\cite{zhao2014automatic} of the TEASER algorithm~\cite{sato2000teasar}. 
This skeletonization algorithm repeatedly uses Dijkstra's algorithm to find the farthest voxel from a seed location. 
Since this algorithm is non-linear in the number of voxels, we downsample the datasets so that there are voxel samples every $\SI{30}{\nano\meter}$ in each dimension.
Empirically, this reduced the running time for skeletonization by $30\times$ with minimal reduction in skeleton accuracy (${\sim}5\%$ fewer branches). 
Fig.~\ref{fig:skeletonization} shows four examples of extracted skeletons (in black). 
These skeletons consist of a sequence of \textit{joints}, locations that are locally a maximum distance from the segment boundary, with line segments connecting successive joints. 
We refer to joints that have only one connected neighbor as \textit{endpoints}. 
We find that approximately 70\% of the segments that are erroneously split have nearby endpoints (Fig.~\ref{fig:merge_candidates}).

Two segments, $s_1$ and $s_2$, receive a corresponding edge if the two following conditions hold.
First, endpoints in either $s_1$ or $s_2$ are within $t_{low}$ nm of any voxel in the other segment.
Second, there are endpoints in $s_1$ and in $s_2$ that are within $t_{high}$ nm of each other.
We store the midpoints between the two endpoints as the center of the potential merge in the set $\mathbb{S}_c$. 
This algorithm produces a set of segments to consider for merging. 
Only these pairs have a corresponding edge in the constructed graph.
We provide an empirical analysis of these parameters on the structure of the graph in the supplemental materials.

\begin{figure}[t]
	\begin{minipage}{0.4\linewidth}
		\includegraphics[width=\linewidth]{./figures/constraint_error.png}
	\end{minipage}
	\hfill
	\begin{minipage}{0.55\linewidth}
		\includegraphics[width=\linewidth]{./figures/constraint_success.png}
	\end{minipage}
	\caption{Two example candidates for merging. The two segments in the left example do not belong to the same neuron as evidenced by the sharp turning radius indicated by the arrow.}
	\label{fig:turn-radii}
\end{figure}
\subsection{Learning-based Edge Weight}
\label{sec:edge-weights}
We assign an edge weight $w_e$ to each edge corresponding to the probability that two nodes belong to the same neuronal process.
We train a 3D CNN model to learn these geometric constraints for valid connection between two segments from labeled volume.
\\~\\
\noindent\textbf{Edge Probability}
To predict the probabilities that two segments belong to the same neuron, we train a feed-forward convolutional network with three \textit{VGG-style} convolution blocks~\cite{chatfield2014return} and two fully connected layers before the final sigmoid activation.

For the input of the network, we extract a cubic region of interest (ROI) around each endpoint $e$ in $\mathbb{S}_c$ as input to the CNN. 
The CNN receives three input channels for every voxel in the ROI around segments $l_1$ and $l_2$. 
The input in all of the channels is in the range $\{-0.5, 0.5\}$. 
The first channel is $0.5$ only if the corresponding voxel has label $l_1$. 
The second channel is $0.5$ only if the corresponding voxel has label $l_2$. 
The third channel is $0.5$ if the corresponding voxel is either $l_1$ or $l_2$.
We do not use the raw EM image information to avoid the need to retrain the network on datasets that have been stained differently or imaged at different resolution. 
This reduces the need for generating costly manually-labeled ground truth.

@@

After graph construction, we segment the graph in a globally consistent manner while enforcing topological constraints on the output.
\\~\\
%\subsubsection{Lifted Multicut}
\noindent\textbf{Lifted Multicut}
After constructing the graph we seek to partition it into labels where every label corresponds to a neuronal process. 
We formulate this graph partitioning problem as a multicut problem.
There are two primary benefits to using a multicut formulation. 
First, the number of segments in the final graph is not predetermined but depends on the input. 
Second, this minimization produces globally consistent solutions (i.e., a boundary remains only if the two corresponding nodes belong to unique segments)~\cite{keuper2015efficient}.

We apply the algorithms of Keuper et al.~\cite{keuper2015efficient} to produce a feasible solution to the multicut problem using greedy additive edge contraction.
Following their example, we employ the generalized lifted multicut formulation.
Traditional multicut solutions only consider the probabilities that two adjacent nodes belong to the same segment. 
In the lifted extension to the problem, we can penalize non-adjacent nodes that belong to different segments. 
These penalties between non-adjacent nodes are called lifted edges. 
Ideally these lifted weights represent the probability that two nodes belong to the same neuron.
However, determining such probabilities is computationally expensive.
We approximate these probabilities by finding the maximal probable path between any two nodes using Dijkstra's algorithm~\cite{keuper2015efficient}.
This is an underestimate of the probability that two nodes belong to the same neuron since it does not consider all possible paths.
Since our graphs are sufficiently small, we can generate lifted edges between all pairs of nodes. 
\\~\\
\noindent\textbf{Edge Weight} 
We need to convert the probabilities into the following weighting scheme to solve the multicut problem with this heuristic~\cite{keuper2015efficient,andres2011probabilistic}.
Given the probability that the nodes belong to the same neuron is $p_e$, the edge weight $w_e$ is defined as
%p_e &=\mbox{CNN}(x_1, x_2) \\
\begin{align}
w_e = \log{\frac{p_e}{1 - p_e}} + \log{\frac{1 - \beta}{\beta}},
\end{align}
where $\beta$ is a tunable parameter that encourages over- or under-segmentation. 
\\~\\
%\subsubsection{Topological Constraints}
\noindent\textbf{Topological Constraints}
By reformulating the segmentation problem as a graph partitioning one, we can enforce some global constraints on our result based on the underlying biology.
Traditional hierarchical clustering algorithms do not rely on such constraints but consider local decisions independently.
We enforce a global constraint that neurons are tree-structured and should not contain cycles. 
The multicut problems returns a series of ``collapsed'' edges between nodes that belong to the same neuron.
We iterate over these edges in order of the probability of merge generated by our CNN. 
We ``collapse'' an edge only if it does not create a cycle in the graph.

### 2018-03-14 papers/eccv2018/3_evaluation.tex
added HP comments

%\noindent\textbf{Training Augmentation.}
Since our input is an existing segmentation of the EM images, there are very few training examples compared to per-pixel classifiers that can train on a unique window for each voxel. 
The Kasthuri dataset represents a region of brain over $\SI[product-units=single]{800}{\micro\meter}^3$ in volume and only yields 640 positive merge examples and 4821 negative ones.
To avoid overfitting our deep networks, we apply the following augmentations on the training examples.
During a single batch, we randomly select ten positive and negative examples. 
With probability 0.5, the example is reflected across the $xy$-plane. 
We then rotate the example by a random angle between $0$ and $360$ degrees using nearest neighbor interpolation. 
The supplemental material contains experiments demonstrating the benefits of this augmentation strategy.
We have 20,000 such examples per epoch.
\\~\\
\noindent\textbf{Graph Partition}
%We assign the edges in our graph a weight $w_e = \log{\frac{p_e}{1 - p_e}} + \log{\frac{1 - \beta}{\beta}}$ where $\beta$ is a tunable parameter. 
%Higher values of $\beta$ encourage over-segmentation.
Figure~\ref{fig:variation-of-information} shows our results for variables $\beta \in [0.5, 0.9]$. 
For our multicut analysis we consider $\beta = 0.5$.

@@

We use precision and recall to evaluate the convolutional neural network and multicut outputs. 
Since our method attempts to only correct \textit{split errors}, we define a true positive as a pair of segments that are correctly merged together after our pipeline.

>>>>

%\noindent\textbf{Training Augmentation.}
Since our input is an existing segmentation of the EM images, there are very few training examples compared to per-pixel classifiers that can train on a unique window for each voxel. 
The Kasthuri dataset represents a region of brain over $\SI[product-units=single]{800}{\micro\meter}^3$ in volume and only yields 640 positive merge examples and 4821 negative ones.
To avoid overfitting our deep networks, we apply the following augmentations on the training examples.
During a single batch, we randomly select ten positive and negative examples. 
With probability 0.5, the example is reflected across the $xy$-plane. 
We then rotate the example by a random angle between $0$ and $360$ degrees using nearest neighbor interpolation. 
The supplemental material contains experiments demonstrating the benefits of this augmentation strategy.
We have 20,000 such examples per epoch.
\\~\\
\noindent\textbf{Graph Partition}
%We assign the edges in our graph a weight $w_e = \log{\frac{p_e}{1 - p_e}} + \log{\frac{1 - \beta}{\beta}}$ where $\beta$ is a tunable parameter. 
%Higher values of $\beta$ encourage over-segmentation.
Figure~\ref{fig:variation-of-information} shows our results for variables $\beta \in [0.5, 0.9]$. 
For our multicut analysis we use $\beta = 0.5$. There are many more lifted edges than adjacent edges. 
To prevent the lifted weights from dominating the objective function we weight each set of edges~\cite{beier2017multicut}.

@@

We use precision and recall to evaluate the convolutional neural network and multicut outputs. 
Since our method only corrects \textit{split errors}, we define a true positive as a pair of segments that are correctly merged together after our pipeline.
